---
title: Sex Difference Summaries
author: Chris Hammill
date: February 28, 2018
output: html_document
---

First we'll load in the longitudinal data

```{r}
suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
})

load("../../cortical_objects_longi20190527.rda")
```

We'll concern ourselves with `civet_deduped`, somewhat deceptively named in
that the longitudinal data is still in there but it has been QC filtered.

## Overall scan breakdown

```{r}
civet_deduped %>% with(table(Dx, sex))

civet_deduped %>%
  group_by(subject) %>%
  with(table(Dx, sex))
```

## Breakdown of scans first vs. later

```{r}
civet_deduped %>%
  group_by(subject) %>%
  mutate(scan_n = length(scan)
       , longi = scan_n > 1) %>%
  filter(!duplicated(subject)) %>%
  with(table(Dx, sex, longi))
```

## Breakdown of proportion of scans that aren't first

```{r}
civet_deduped %>%
  group_by(subject) %>%
  mutate(scan_n = length(scan)
       , longi = scan_n > 1) %>%
  filter(!duplicated(subject)) %>%
  with(tapply(longi, list(Dx, sex), mean))
```

## Age breakdown by group

Mean ages

```{r}
civet_deduped %>%
  group_by(Dx, sex) %>%
  summarize(mean_age = mean(age_scan))
```

Age histograms

```{r}
civet_deduped %>%
  mutate(sex_dx = paste(sex, Dx, sep = ":")) %>%
  ggplot(aes(x = age_scan, group = sex_dx)) +
  geom_histogram() +
  facet_wrap(~ sex_dx)
ggsave("age_hists.png", width = 12, height = 6)

civet_deduped$age_scan %>% range
```

## IQ breakdown by group

IQ means

```{r}
civet_deduped %>%
  filter(!duplicated(subject)) %>%
  group_by(Dx, sex) %>%
  summarize(mean_iq = mean(iq, na.rm = TRUE))
```

IQ histograms

```{r}
civet_deduped %>%
  filter(!duplicated(subject)) %>%
  mutate(sex_dx = paste(sex, Dx, sep = ":")) %>%
  ggplot(aes(x = iq, group = sex_dx)) +
  geom_histogram() +
  facet_wrap(~ sex_dx)
```




