---
title: generate_model_selection_assets
author: Chris Hammill
date: December 21, 2017
output: html_document
---

## Load up

Load in required packages

```{r}
knitr::opts_chunk$set(cache.lazy = FALSE)
suppressPackageStartupMessages({
    library(autismSexDifferences)
    library(RMINC)
    library(purrr)
    library(dplyr)
    library(mice)
    library(batchtools)
    library(tidyr)
    library(ggplot2)
})
```


## Data ingest

Pull in data

```{r pull_data, cache = TRUE}
load("../cortical_objects_longi20171221.rda")
```

## Setup Models

First we'll set up the model sets for model selection.

We'll make the two model formula sets, with and without iq

```{r model_form, cache = TRUE}
model_forms <-
    c(nint = ~ iq + sex + Dx + bv + age_scan + Dx:sex + new_scanner + (1 | subject)
    , nint_crb = ~ iq + sex + Dx + crbv + age_scan + Dx:sex + new_scanner + (1 | subject)
    , nint_ttrb = ~ iq + sex + Dx + ttrbv + age_scan + Dx:sex + new_scanner + (1 | subject)
    , pnint = ~ iq + sex + Dx + bv + poly(age_scan,2) + Dx:sex + new_scanner + (1 | subject)
    , pnint_crb = ~ iq + sex + Dx + crbv + poly(age_scan,2) + Dx:sex + new_scanner + (1 | subject)
    , pnint_ttrb = ~ iq + sex + Dx + ttrbv + poly(age_scan,2) + Dx:sex + new_scanner + (1 | subject)
    , nex = ~ iq + sex + Dx + bv + age_scan + Dx:sex + age_scan:sex + new_scanner + (1 | subject)
    , nex_crb = ~ iq + sex + Dx + crbv + age_scan + Dx:sex + age_scan:sex + new_scanner + (1 | subject)
    , nex_ttrb = ~ iq + sex + Dx + ttrbv + age_scan + Dx:sex + age_scan:sex + new_scanner + (1 | subject)
    , nage = ~ iq + sex + Dx + bv + age_scan + Dx:sex + bv:sex + new_scanner + (1 | subject)
    , nage_crb = ~ iq + sex + Dx + crbv + age_scan + Dx:sex + crbv:sex + new_scanner + (1 | subject)
    , nage_ttrb = ~ iq + sex + Dx + ttrbv + age_scan + Dx:sex + ttrbv:sex + new_scanner + (1 | subject)
    , st = ~ iq + sex + Dx + bv + age_scan + Dx:sex + bv:sex + age_scan:sex + new_scanner + (1 | subject)
    , crb = ~ iq + sex + Dx + crbv + age_scan + Dx:sex + crbv:sex + age_scan:sex + new_scanner + (1 | subject)
    , ttrb = ~ iq + sex + Dx + ttrbv + age_scan + Dx:sex + ttrbv:sex + age_scan:sex + new_scanner + (1 | subject)
    , page = ~ iq + sex + Dx + bv + poly(age_scan,2) + Dx:sex + bv:sex + poly(age_scan,2):sex + new_scanner + (1 | subject)
    , page_crb = ~ iq + sex + Dx + crbv + poly(age_scan,2) + Dx:sex + crbv:sex + poly(age_scan,2):sex + new_scanner + (1 | subject)
    , page_ttrb = ~ iq + sex + Dx + ttrbv + poly(age_scan,2) + Dx:sex + ttrbv:sex + poly(age_scan,2):sex + new_scanner + (1 | subject))

model_forms_noiq <- lapply(model_forms, function(m) update(m,  ~ . - iq))

models_set <-
  list(iq = model_forms
     , noiq = model_forms_noiq)
```

## Generate Full Experiment

For the mixed effects version, I'm going to follow the same expansion as the non mixed effects version
but winnow the pool down to:

1. All: both matched and modelled    (5)
2. All: neither matched nor modelled (1)
3. LT85: neither                     (1)
4. LT100: neither                    (1)
5. GT85: both                        (5)
6. GT100: both                       (5)

For a total of 18 experiments, 4 measures each. With 36 models to select from, 1000 randomizations,
and 1 final model. Each taking approximately half an hour to fit is going to need 37000 hours of
single core compute.

## Imputation

First we need to impute iq (for the analyses that match or model IQ)

```{r imputation, cache = TRUE, dependson = "pull_data"}
imputed_sets <-
    model_data %>%
    select(age_scan, bv, sex, Dx, iq) %>%
    mice %>%
    mids_to_dfs %>%
    lapply(mutate
         , subject = model_data$subject
         , new_scanner = model_data$new_scanner
         , crbv = model_data$crbv
         , ttrbv = model_data$ttrbv
         , Dx = as.numeric(factor(Dx, c("CTRL", "ASD"))) - 1)

```

## Generate IQ Partitions

Now I need to generate the splits needed for the subgrouping

```{r iq_groups, dependson = "imputation"}
iq_scale <- sd(civet_deduped$iq, na.rm = TRUE)
iq_center <- mean(civet_deduped$iq, na.rm = TRUE)

imputed_sets <-
  imputed_sets %>%
  lapply(function(f){
    mutate(f
         , iq_native = iq * iq_scale + iq_center)
  })     
```

## Matching

Now that we have the imputed sets we can perform the matching.

```{r dist_calc, cache = TRUE, dependson = "imputation"}

experiment_frame <-
  crossing(match_iq = c(TRUE, FALSE)
         , data_frame(set = imputed_sets
                    , set_number = seq_along(imputed_sets))
         , data_frame(pred =
                        list(function(x) TRUE
                           , function(x) x <= 85
                           , function(x) x > 85
                           , function(x) x <= 100
                           , function(x) x > 100
                             )
                      )) %>% 
  mutate(w_iq = ifelse(match_iq, 1/4, 0)
       , w_bv = 1/2
       , split = sapply(pred, function(x) deparse(body(x)))
       , experiment = paste0("match", match_iq, "_", set_number, "_", split)) %>%
  filter((split == "TRUE") 
       | (split == "x <= 85"  & !match_iq) 
       | (split == "x <= 100" & !match_iq) 
       | (split == "x > 85"   &  match_iq) 
       | (split == "x > 100"  &  match_iq)) %>%
  filter(match_iq | set_number == 1)

subject_distances <-
  experiment_frame %>%
  pmap(function(set,w_iq,w_bv, pred, ...)
    create_dist_mat(data = filter(set, pred(iq_native) | Dx == 0)
                  , w_iq = w_iq, w_bv = w_bv)) %>%
  data_frame(distances = ., experiment = experiment_frame$experiment)

```

Now to do the actual matching

```{r matching, cache = TRUE, dependson = "dist_calc"}
matched_sets <-
  experiment_frame %>%
  pmap(function(set, pred, experiment, ...){
    exp <- experiment
    distance <-
      subject_distances %>%
      filter(experiment == exp) %>%
      .$distances %>%
      first

    full_match(filter(set, pred(iq_native) | Dx == 0)
             , distance)
    })

sets_frame <-
  mutate(experiment_frame
       , matched_set = matched_sets)
```

## Add outcome measures

Now cross the experiment frame with the matches

```{r add_outcomes, cache = TRUE, dependson = "matching"}
measures <-
  list(thickness = thickness
     , area = area
     , volume = volume
     , mean_curv = mean_curv)

measures_frame <- 
  crossing(experiment = experiment_frame$experiment
         , measures = c("thickness", "area", "volume", "mean_curv"))
```

## Model Selection Experiment

Make a test grid for model selection

```{r model_selection_grid, cache = TRUE, dependson = c("add_outcomes", "model_form")}
model_selection_frame <-
  experiment_frame %>%
  select(-set) %>%
  inner_join(measures_frame, by = "experiment")

## This line differs in that there is no matched not modelled or vice-versa
## So I only need the two combinations
models_frame <- 
  data_frame(model_iq = c(TRUE, FALSE)
           , match_iq = c(TRUE, FALSE) 
           , model = models_set) %>%
rowwise() %>%
  do({
    as_data_frame(.) ## this expands out the 18 models
  })

model_selection_frame <-  
  inner_join(model_selection_frame, models_frame, by = "match_iq") 
```

## Write Out Model Selection Assets

Now write out all of these objects to be read in by the
next portion of the analysis

```{r output, cache = TRUE, dependson = "model_selection_grid"}
save(measures_frame = measures_frame
   ,  measures = measures
   , model_selection_frame = model_selection_frame
   , sets_frame = sets_frame
   , experiment_frame = experiment_frame
   , imputed_sets = imputed_sets
   , file = "model_selection_assets.rda"
     )
```
