---
title: output_results
author: Chris Hammill
date: December 12, 2017
output: html_document
---

## Load up

Load in required packages

```{r}
suppressPackageStartupMessages({
    library(autismSexDifferences)
    library(RMINC)
    library(purrr)
    library(dplyr)
    library(mice)
    library(batchtools)
    library(tidyr)
    library(ggplot2)
})
```

## Get Model Selection Results

```{r load_model_sel, cache = TRUE}
load("model_selection_results.rda")
```
## Get Randomization Results

```{r load_rand_res, cache = TRUE}
rand_res <- readRDS("./original_merged_experiment.rds") #remove orig on revert

rand_res <-
  rand_res %>%
  mutate(res = lapply(res, first)) %>% #remove on revert
  mutate(concordance = lapply(res, getElement, "concordance")
       , eff_cor = lapply(res, getElement, "eff_cor")
       , max_mb = sapply(res, getElement, "max_mb")
       , max_fb = sapply(res, getElement, "max_fb")
       , max_meff = sapply(res, getElement, "max_meff")
       , max_feff = sapply(res, getElement, "max_feff"))
```

## Test some plots

Extract test group

```{r extract_test, cache = TRUE, dependson = "load_rand_res"}
test_data <- 
  rand_res %>%
  nest %>%
  slice(4) %>%
  unnest
```

Test random line version

```{r test_random_concordance_lines, cache = TRUE, dependson = "extract_test"}
test_data_munged <-
  test_data %>%
  select(-eff_cor, -res) %>%
  mutate(is_shuffled = !is.na(shuffle)) %>%
  mutate(step = list(seq(1, 500))) %>%
  unnest

bounds <-
  test_data_munged %>%
  filter(is_shuffled) %>%
  filter(step != 500) %>%
  ungroup %>%
  group_by(step) %>%
  summarize(ub = quantile(concordance, .975)
          , lb = quantile(concordance, .025))

test_data_munged %>%
  filter(!is_shuffled | shuffle %in% sample(1:1001, 100)) %>%
  ggplot(aes(x = step, y = concordance, color = is_shuffled, group = shuffle)) +
  geom_ribbon(data = bounds, aes(x = step, ymin = lb, ymax = ub
                               , y = NULL, group = NULL, color = NULL)
            , fill = "grey") +
  geom_line() 
```

After consulting with Ben and Anthony, it looks like I'm going to present
it this way with randomization intervals for the whole data set plus
a sample of 100 randomization lines.

Test with effective correlation as well

```{r test_random_effcor_lines, cache = TRUE, dependson = "extract_test"}
test_data_munged <-
  test_data %>%
  select(-concordance, -res) %>%
  mutate(is_shuffled = !is.na(shuffle)) %>%
  mutate(quantile_steps =
           list(c(0
                , seq(.1, .9, 0.1)
                , seq(.9, .99, .01)
                , seq(.99, .999, .001)))) %>%
  unnest

bounds <-
  test_data_munged %>%
  filter(is_shuffled) %>%
  ungroup %>%
  group_by(quantile_steps) %>%
  summarize(ub = quantile(eff_cor, .975)
          , lb = quantile(eff_cor, .025))

test_data_munged %>%
  filter(!is_shuffled | shuffle %in% sample(1:1001, 100)) %>%
  ggplot(aes(x = quantile_steps, y = eff_cor, color = is_shuffled, group = shuffle)) +
  geom_ribbon(data = bounds, aes(x = quantile_steps, ymin = lb, ymax = ub
                               , y = NULL, group = NULL, color = NULL)
            , fill = "grey") +
  geom_line() 
```

Awesome, everything seems to be working. Let's do this for all of them.

## Plot Functions

Create some simple plots of the randomization dists

```{r plot_functions, cache = TRUE}
plot_concordance <-
  function(df_chunk){
    data_munged <-
      df_chunk %>%
      select(-eff_cor, -res) %>%
      mutate(is_shuffled = !is.na(shuffle)) %>%
      mutate(step = list(seq(1, 500))) %>%
      unnest

    bounds <-
      data_munged %>%
      filter(is_shuffled) %>%
      filter(step != 500) %>%
      ungroup %>%
      group_by(measures, step) %>%
      summarize(ub = quantile(concordance, .975)
              , lb = quantile(concordance, .025))

    data_munged %>%
      filter(!is_shuffled | shuffle %in% sample(1:1001, 100)) %>%
      ggplot(aes(x = step, y = concordance, color = is_shuffled, group = shuffle)) +
      geom_ribbon(data = bounds, aes(x = step, ymin = lb, ymax = ub
                                   , y = NULL, group = NULL, color = NULL)
                , fill = "grey") +
      geom_line() 
  }

plot_similarity <-
  function(df_chunk){
    data_munged <-
      df_chunk %>%
      select(-concordance, -res) %>%
      mutate(is_shuffled = !is.na(shuffle)) %>%
      mutate(quantile_steps =
               list(c(0
                    , seq(.1, .9, 0.1)
                    , seq(.9, .99, .01)
                    , seq(.99, .999, .001)))) %>%
      unnest

    bounds <-
      data_munged %>%
      filter(is_shuffled) %>%
      ungroup %>%
      group_by(measures, quantile_steps) %>%
      summarize(ub = quantile(eff_cor, .975)
              , lb = quantile(eff_cor, .025))

   data_munged %>%
      filter(!is_shuffled | shuffle %in% sample(1:1001, 100)) %>%
      ggplot(aes(x = quantile_steps, y = eff_cor, color = is_shuffled, group = shuffle)) +
      geom_ribbon(data = bounds, aes(x = quantile_steps, ymin = lb, ymax = ub
                                   , y = NULL, group = NULL, color = NULL)
                , fill = "grey") +
      geom_line() 
  }

create_fig_name <-
  function(root, df_chunk){
    first_row <- purrr::transpose(df_chunk) %>% first
    names(first_row) <- names(df_chunk)

    iq_match <-
      `if`(first_row$match_iq
         , "iqMatched"
         , "iqNotMatched")

    iq_model <-
      `if`(first_row$iq_modelled
         , "iqModelled"
         , "iqNotModelled")

    measure <- first_row$measures

    split <- switch(as.character(first_row$split)
                 ,  `x > 100` = "ageGT100"
                 , `x <= 100` = "ageLTE100"
                 , `x > 85` = "ageGT85"
                 , `x <= 85` = "ageLTE85"
                 , `TRUE` = "ageAny")

    paste0(
      paste(root, split, measure, iq_match, iq_model, sep = "_")
    , ".png")
  }
```

Now to run them

```{r generate_figures, cache = TRUE, dependson = c("plot_functions", "load_rand_res")}
if(!file.exists("figures"))
  dir.create("figures")

walk(seq_len(n_groups(rand_res)), function(i){
  data <-
    rand_res %>%
    nest %>%
    slice(i) %>%
    unnest
    
  conc_fig_name <-
    file.path("figures"
            , create_fig_name("concordance", data))

  png(conc_fig_name, width = 2048, height = 1024)
  print(plot_concordance(data))
  dev.off()

  sim_fig_name <-
    file.path("figures"
            , create_fig_name("similarity", data))

  png(sim_fig_name, width = 2048, height = 1024)
  print(plot_similarity(data))
  dev.off()
})
```

```{r generate_four_panels, cache = TRUE, dependson = c("generate_figures")}
ngrps <-
  ungroup(rand_res) %>% group_by(match_iq, iq_modelled, split) %>% n_groups

walk(seq_len(ngrps), function(i){
  data <-
    rand_res %>%
    ungroup %>%
    group_by(match_iq, iq_modelled, split) %>%
    nest %>%
    slice(i) %>%
    unnest
    
  conc_fig_name <-
    file.path("figures"
            , paste0("four_"
                   , sub("png", "pdf"
                         , create_fig_name("concordance", data))))

  pdf(conc_fig_name, width = 24, height = 12)
  print(
    plot_concordance(data) +
    facet_wrap(~ measures) +
    ggtitle(create_fig_name("concordance", data)) +
    guides(colour = FALSE) +
    theme(text = element_text(size = 34))
  )
  dev.off()

  sim_fig_name <-
    file.path("figures"
            , paste0("four_"
                   , sub("png", "pdf"
                       , create_fig_name("similarity", data))))

  pdf(sim_fig_name, width = 24, height = 12)
  print(
    plot_similarity(data) +
    facet_wrap(~ measures) +
    ggtitle(create_fig_name("similarity", data)) +
    guides(colour = FALSE) +
    theme(text = element_text(size = 34))
  )
  dev.off()
})

system("touch figures_done.txt")
```


