---
title: run_spatial_analyses
author: Chris Hammill
date: December 28, 2017
output: html_document
---

## Load up

Load in required packages

```{r}
knitr::opts_chunk$set(cache.lazy = FALSE)
suppressPackageStartupMessages({
    library(autismSexDifferences)
    library(RMINC)
    library(purrr)
    library(dplyr)
    library(mice)
    library(batchtools)
    library(tidyr)
    library(ggplot2)
})
```


## Data ingest

Pull in data

```{r pull_data, cache = TRUE}
load("../cortical_objects_longi20180115.rda")
load("model_selection_assets.rda")
load("model_selection_results.rda")
```

## Set up randomization grid

Now to join the best models back to the experiment
frame

```{r generate_experiment_frame, cache = TRUE}
randomization_experiments <-
  inner_join(best_models, experiment_frame %>% select(-set)
           , by = c("match_iq", "split"))

if(nrow(randomization_experiments) != 72)
  stop("merging went wrong")

randomization_experiments <-
  crossing(randomization_experiments, shuffle = c(1:1000, NA))
```

## Set up analysis function

Here is the work-horse function for computing the randomization

```{r setup_function, cache = TRUE}
get_data <- function(match_iq, set_number, split, measurement){

  ## Rename for use in filter
  iq <- match_iq
  sn <- set_number
  sp <- split
  
  data <-
    sets_frame %>%
    filter(match_iq == iq
         , set_number == sn
         , split == sp)

  if(nrow(data) != 1)
    stop("something is wrong with your sets frame")

  full_set <- data$set[[1]]
  matched_set <- data$matched_set[[1]]
  pred <- data$pred[[1]]
  
  filter_vec <- pred(full_set$iq_native) | full_set$Dx == 0
  anat <- measures[[measurement]][,filter_vec]

  if(ncol(anat) != nrow(matched_set))
    stop("The filtration didn't work")

  list(data = matched_set
     , anat = anat
     , filter_vec = filter_vec)
}

fit_model <- function(model, data){
  weights <- data$data$weight
  anatLmer(model, data = data$data
         , anat = t(data$anat), weights = weights)
}

purge_environments <- function(mod){
  environment(attributes(mod)$mincLmerList[[1]]$formula) <- NULL
  environment(attr(attributes(mod)$mincLmerList[[1]]$fr, "formula")) <- NULL
  environment(attr(attributes(mod)$mincLmerList[[1]]$fr, "terms")) <- NULL
  
  mod
}

run_randomization <-
  function(i){
    gc()
    gc()

    mes <- randomization_experiments$measures[i]
    form <- randomization_experiments$model_string[[i]]
    set_n <- randomization_experiments$set_number[[i]]
    sp <- randomization_experiments$split[i]
    miq <- randomization_experiments$match_iq[i]
    
    data <- get_data(match_iq = miq, set_number = set_n
                   , split = sp, measurement = mes)

    shuf_ind <- randomization_experiments$shuffle[i]
    
    if(!is.na(shuf_ind)){
      ##shuf <- shuffles[,shuf_ind]
      ##shuf <- shuf[shuf <= nrow(data$data)]
      
      data$data$sex <-
        ifelse(new_sexes[data$filter_vec,shuf_ind] == "M", 0, 1)
      ##data$data$sex[shuf]
    } else {
      data$data$sex <- ifelse(data$data$sex == "M", 0, 1)
    }

    
    mod <- fit_model(as.formula(form), data)
    attr(mod, "anat") <- NULL
    mod <- purge_environments(mod)
    
    mod
  }

process_randomization <- function(mod){
  max_t <- max(abs(mod[,"tvalue-Dx"])
             , abs(mod[,"tvalue-sex:Dx"]))
  
  steps <- seq(0,max_t, length.out = 500)

  concordance <-
    sapply(steps, function(t){
      verts <-
        abs(mod[,"tvalue-Dx"]) > t |
        abs(mod[,"tvalue-sex:Dx"]) > t

      sum(sign(mod[verts,"tvalue-Dx"]) ==
          sign(mod[verts,"tvalue-sex:Dx"])) /
        sum(verts)                
    })

  male_eff <- mod[,"beta-Dx"]
  female_eff <- mod[,"beta-Dx"] + mod[,"beta-sex:Dx"]

  quantile_steps <- c(0
                    , seq(.1, .9, 0.1)
                    , seq(.9, .99, .01)
                    , seq(.99, .999, .001))

  mq <- quantile(abs(male_eff), quantile_steps)
  fq <- quantile(abs(female_eff), quantile_steps)


  eff_cor <-
    mapply(function(mq, fq){
      male_eff[abs(male_eff) < mq] <- 0
      female_eff[abs(female_eff) < fq] <- 0
      cor(female_eff, male_eff)
    }, mq = mq, fq = fq)

  max_mb <- max(abs(mod[,"tvalue-Dx"]))
  max_fb <- max(abs(mod[,"tvalue-sex:Dx"]))
  max_meff <- max(abs(mod[,"beta-Dx"]))
  max_feff <- max(abs(mod[,"beta-sex:Dx"]))


  gc()
  gc()
  
  list(concordance = concordance
     , eff_cor = eff_cor
     , max_mb = max_mb
     , max_fb = max_fb
     , max_meff = max_meff
     , max_feff = max_feff)
}


```
## Set up registry

Now to intialize the registry

```{r init_registry, cache = TRUE, dependson = c("setup_function", "generate_experiment_frame")}
sa_reg <-
    makeRegistry("spatial_analyses_fixed"
               , packages = c("autismSexDifferences"
                            , "RMINC"
                            , "purrr"
                            , "dplyr"))

sa_reg$cluster.functions <-
  makeClusterFunctionsTORQUE("torque.tmpl")

sa_reg$default.resources <- 
    list(nodes = 1
       , memory = "12G"
       , walltime = "08:00:00"
       , max.concurrent.jobs = 2000)

batchExport(reg = sa_reg
          , export = list(measures = measures
                        , randomization_experiments = randomization_experiments
                        , sets_frame = sets_frame
                        , fit_model = fit_model
                        , new_sexes = new_sexes
                        , get_data = get_data
                        , purge_environments = purge_environments))

sa_reg <- sa_reg
```

## Create Jobs

Add the jobs to the registry

```{r job_creation, cache = TRUE, dependson = "init_registry"}
job_ids <-
  batchMap(reg = sa_reg
         , run_randomization
         , seq_len(nrow(randomization_experiments)))

randomization_experiments$job_id <- job_ids$job.id

## job_ids[, chunk :=
##             chunk(seq_len(nrow(randomization_experiments))
##                 , chunk.size = 4)]

sa_reg <- sa_reg
```

## Test Job

Run a test job

```{r test_job, cache = TRUE, dependson = "job_creation"}
invisible(testJob(reg = sa_reg, 20000)) 
```

## Run Jobs

Run the jobs and wait

```{r job_submission, cache = TRUE, dependson = "test_job", eval = FALSE}
submitJobs(reg = sa_reg, job_ids)
waitForJobs(reg = sa_reg)
```

## Fix jobs that failed

```{r job_fixes, cache = TRUE, dependson = "job_submission"}
sa_reg <- loadRegistry("spatial_analyses_fixed", writeable = TRUE)

sa_reg$cluster.functions <-
  makeClusterFunctionsTORQUE("torque.tmpl")

sa_reg$default.resources <- 
    list(nodes = 1
       , memory = "12G"
       , walltime = "08:00:00"
       	 , max.concurrent.jobs = 2000)
	 
not_done <- findNotDone(reg = sa_reg)
submitJobs(reg = sa_reg, not_done)
waitForJobs(reg = sa_reg)
```

## Submit The NA shuffles

Stupid crossing threw away my NAs

```{r run_extras, cache = TRUE, dependson = "job_fixes"}
## unshuffled_frame <-
##   randomization_experiments %>%
##   filter(shuffle == 1) %>%
##   mutate(shuffle = NA)

## f_reg <-
##     makeRegistry("spatial_analyses_fixup_fixed"
##                , packages = c("autismSexDifferences"
##                             , "RMINC"
##                             , "purrr"
##                             , "dplyr"))

## f_reg$cluster.functions <-
##   makeClusterFunctionsTORQUE("torque.tmpl")

## f_reg$default.resources <- 
##     list(nodes = 1
##        , memory = "12G"
##        , walltime = "08:00:00"
##        , max.concurrent.jobs = 2000)

## batchExport(reg = f_reg
##             , export = list(measures = measures
##                           , randomization_experiments = unshuffled_frame
##                           , sets_frame = sets_frame
##                           , fit_model = fit_model
##                           , new_sexes = new_sexes
##                           , get_data = get_data))

## f_job_ids <-
##   batchMap(reg = f_reg
##          , analyze_randomization
##          , seq_len(nrow(unshuffled_frame)))

## submitJobs(reg = f_reg, f_job_ids)
## waitForJobs(reg = f_reg)
```

## Flag Finished

```{r finalize, cache = TRUE, dependson = "fixup"}
system("touch spatial_analyses_finished.txt")
```
