---
title: vertexwise_results
author: Chris Hammill
date: March 05, 2018
output: html_document
---

Now I want to look at the results of these analyses. 

First I need some new functions, combining imputations is relatively simple
but I will need to deconstruct the lmer objects in order to get p-values.
So let's start by loading in the data and then presenting the necessary functions

## Load up

Load in required packages

```{r}
knitr::opts_chunk$set(cache.lazy = FALSE)
suppressPackageStartupMessages({
    library(autismSexDifferences)
    library(RMINC)
    library(purrr)
    library(dplyr)
    library(mice)
    library(batchtools)
    library(tidyr)
    library(ggplot2)
})
```

## Data ingest

First let's load in the needed assets 

```{r pull_data, cache = TRUE}
load("../cortical_objects_longi20180115.rda")
load("model_selection_assets.rda")
load("model_selection_results.rda")
reg <- loadRegistry("./vertexwise_analyses/")
```

## Functions

```{r functions, cache = TRUE, dependson = "pull_data"}
get_se <- function(model, eff_name){
  model %>%
    { .[, paste0("beta-", eff_name)] /
        .[,paste0("tvalue-", eff_name)] }
}

process_lmer <- function(model, effects = c("sex2", "sex2:Dx")){
  n <- nrow( attributes(model)$data )
  lapply(effects
       , function(eff){
         cbind(model[, paste0("beta-", eff)]
             , (get_se(model, eff) * sqrt(n))^2 ) %>%
         `colnames<-`(paste0(c("beta-", "v-"), eff))
         }) %>%
    Reduce(cbind, .) %>%
    `attr<-`("n", n) 
}

merge_lmers <- function(processed_mods){
  n <- length(processed_mods)
  m <- ncol(processed_mods[[1]])
  nms <- colnames(processed_mods[[1]])
  
  means <- 
    Reduce(
      function(acc, pm){
        pm/n + acc
      }, processed_mods, 0)
  
  vars <-
    Reduce(
      function(acc, pm){
        (pm - means)^2 + acc
      }, processed_mods, 0
    ) / (n - 1)

  res <- cbind(means, vars)
  attr(res, "n") <- attr(processed_mods[[1]], "n")

  colnames(res) <- c(nms, paste0("mv-", nms))
  res
}

process_merged_lmers <- function(merged_lmer, m = 5){
  nm <- colnames(merged_lmer)
  effs <-
    grep("^beta-", nm, value = TRUE) %>%
    sub("^beta-", "", .)

  betas <- paste0("beta-", effs)
  vs <- paste0("v-", effs)
  mv_betas <- paste0("mv-beta-", effs)

  eff_betas <- merged_lmer[,betas, drop = FALSE]
  eff_sds <- sqrt(merged_lmer[,vs, drop = FALSE] +
                  (1 + 1/m) * merged_lmer[,mv_betas, drop = FALSE]^2)
  eff_se <- eff_sds / sqrt(attr(merged_lmer, "n"))

  res <- cbind(eff_betas, eff_betas / eff_se)
  colnames(res) <- c(betas, paste0("tvalue-", effs))

  res
}

process_and_replace <- function(models, effects = NULL, debug = FALSE){
  n <- length(models)
  if(debug && (! n %in% c(1,5)))
    stop("Strange group size detected")

  if(n == 1)
    return(models)

  if(is.null(effects))
    effects <-
      colnames(models[[1]]) %>%
      grep("^beta-", ., value = TRUE) %>%
      sub("beta-", "", .)
  
  pooled_stats <- 
    map(models, process_lmer, effects = effects) %>%
    merge_lmers() %>%
    process_merged_lmers(m = n)

  fixed_model <- models[[1]]
  fixed_model[, colnames(pooled_stats)] <- pooled_stats

  fixed_model
}

## Test that my pooling yeilds equivalent results, and yes they do!

## response <- rnorm(1045)
## lmod <- map(useful_sets$matched_set
##           , ~ anatLm(~ sex + Dx + sex:Dx, data = ., anat = matrix(response)))
## lms <- as.mira(map(useful_sets$matched_set, ~ lm(response ~ sex + Dx + sex:Dx, data = .)))
## lmod %>%
##   map(function(l){
##     attributes(l)$mincLmerList[[1]$fr <- useful_sets$matched_set[[1]]
##     l
##   }) %>%
##   map(process_lmer) %>%
##   merge_lmers %>%
##   process_merged_lmers

## summary(pool(lms))
```

## Construct experiment frame

Equivalent to the same code from `run_spatial_analysis`

```{r generate_experiment_frame, cache = TRUE, dependson = "functions"}
experiment_frame_filtered <-
  experiment_frame %>%
  ungroup %>%
  filter(!grepl("<", split))

model_frame <-
  inner_join(ungroup(best_models), experiment_frame_filtered %>% select(-set)
           , by = c("match_iq", "split")) %>%
  mutate(job = 1:n())

if(nrow(model_frame) != 64)
  stop("merging went wrong")
```

now I need to get a group of them to test on

```{r test_processing, cache = TRUE, eval = FALSE}
test_group <- 
  model_frame %>%
  filter(!(!match_iq | split == "TRUE")) %>%
  group_by(match_iq, split, measures) %>%
  nest %>%
  slice(1) %>%
  unnest

#test_res <- reduceResultsList(test_group$job, reg = reg)
```

## Figure code

```{r figure_code, cache = TRUE}
show_effect <-
  function(model, column, range, file){
    right_vals <- model[rep(c(TRUE,FALSE), each = nrow(model)/2),column]
    left_vals <- model[rep(c(FALSE, TRUE), each = nrow(model)/2),column]

    left_coefs <- rep(0, length(aal_left_mask))
    left_coefs[aal_left_mask] <- left_vals

    right_coefs <- rep(0, length(aal_right_mask))
    right_coefs[aal_right_mask] <- right_vals


    obj_montage(surface_left, surface_right, left_coefs, right_coefs
              , colour_range = range
              , symmetric = TRUE
              , output = file)
  }
```

## Process models

```{r get_models, cache = TRUE, dependson = "generate_experiment_frame"}
grouped_models <-
  model_frame %>%
  group_by(match_iq, split, measures)

ngroups <- n_groups(grouped_models)

process_group <- function(grp){
  print(grp$job)
  res <- reduceResultsList(grp$job
                         , function(m){
                           attributes(m)[c("anat"
                                         , "mincLmerList")] <-  NULL
                           gc()
                           m
                         }
                       , reg = reg)
  if(length(res) > 1){
    res <- process_and_replace(res, c("sex2", "sex2:Dx", "Dx"))
  } else {
    res <- res[[1]]
  }

  res <- res[, sapply(c("sex2", "sex2:Dx", "Dx"),
                      function(s)
                        paste0(c("beta-", "tvalue-"), s))
             ]

  attributes(res)$anat <- NULL

  return(res)
}

results <-
  grouped_models %>%
  do(res = process_group(.))
```

## FDR

Now that we have the results, we're going to go through and do
FDR correction on the diagnosis, sex, and interaction effects.
For this I'm going to use 

```{r get_thresh, cache = TRUE, dependson = "get_models"}
results_with_thresh <-
  results %>%
  ungroup %>%
  mutate(res = map(res, function(r){
    cols <- grep("tvalue-", colnames(r), value = TRUE)
    effs <- sub("tvalue-", "", cols)
    ts <- r[,cols]
    qs <- apply(ts, 2, function(x) fdrtool::fdrtool(x, plot = FALSE)$qval)
    new_res <- cbind(r, qs)
    colnames(new_res) <- c(colnames(r), paste0("qvalue-", effs))
    new_res
  })
, cutoffs = map(res, function(r){
  qnames <- grep("qvalue-", colnames(r), value = TRUE)
  eff <- sub("qvalue-", "", qnames)
  thresholds <- 
    sapply(eff, function(n){
      ts <- r[, paste0("tvalue-", n)]
      qs <- r[, paste0("qvalue-", n)]
      min(abs(ts)[qs < .10])
    })
    
  as.list(thresholds) %>%
    setNames(paste0("thresh-", qnames)) %>%
    as_data_frame
})) %>%
unnest(cutoffs)
```

## Snapshots

Now we're going to take some snapshots, first let's create a directory if it doesn't
exist yet. The walk the results and snapshot

```{r generate_snaps, cache = TRUE, dependson = "get_thresh"}
if(!file.exists("vertexwise_snaps"))
  dir.create("vertexwise_snaps")

results_with_thresh %>%
  pwalk(function(measures, match_iq, split, res, ...){
    .dots <- list(...)
    filename <- paste(`if`(match_iq, "match", "nomatch")
                    , case_when(split == "TRUE" ~ "iq-all"
                              , split == "x > 100" ~ "iq-gt100"
                              , split == "x > 85" ~ "iq-gt85")
                    , measures
                    , sep = "_")
    
    effs <- c("Dx", "sex2", "sex2:Dx")
    walk(effs, function(eff){
      tval <- res[, paste0("tvalue-", eff)]
      thresh <- getElement(.dots, paste0("thresh-qvalue-", eff))
      if(!is.finite(thresh)) thresh <- 0
      show_effect(res, paste0("tvalue-", eff), range = c(thresh, 5)
                , file = file.path("vertexwise_snaps"
                                 , paste0(filename, "_tvalue-"
                                        , sub(":", "-", eff)
                                        , ".png")))
    })
  })
```

## Output data

output the thresholds

```{r output_thresholds, cache = TRUE, dependson = "get_thresh"}
results_with_thresh %>%
  select(-res) %>%
  write.csv(paste0(Sys.Date(), "_vertexwise-fdr-thresholds.csv"), row.names = FALSE)
```

output the pooled data

```{r output_pooled_res, cache = TRUE, dependson = "get_thresh"}
results_with_thresh %>%
  saveRDS(paste0(Sys.Date(), "_pooled-vertexwise-res.rds"))
```
