---
title: run_spatial_analyses
author: Chris Hammill
date: December 28, 2017
output: html_document
---

## Load up

Load in required packages

```{r}
knitr::opts_chunk$set(cache.lazy = FALSE)
suppressPackageStartupMessages({
    library(autismSexDifferences)
    library(RMINC)
    library(purrr)
    library(dplyr)
    library(mice)
    library(batchtools)
    library(tidyr)
    library(ggplot2)
})
```


## Data ingest

Pull in data

```{r pull_data, cache = TRUE}
load("../cortical_objects_longi20180115.rda")

complete_measures <- ## needs to be done before loading the next rdas
  model_data %>%
  select(##matches("lobeVolume_")
    Vermal_I_II:right.ventral.posterior.nucleus) %>%
  as.matrix %>%
  complete.cases

load("model_selection_assets.rda")
load("model_selection_results.rda")
```

## Set up randomization grid

Now to join the best models back to the experiment
frame

```{r generate_experiment_frame, cache = TRUE}
randomization_experiments <-
  inner_join(best_models, experiment_frame %>% select(-set)
           , by = c("match_iq", "split"))

if(nrow(randomization_experiments) != 18)
  stop("merging went wrong")

randomization_experiments <-
  crossing(randomization_experiments, shuffle = c(1:1001, NA))
```

## Set up analysis function

Here is the work-horse function for computing the randomization

```{r setup_function, cache = TRUE}
get_data <- function(match_iq, set_number, split, measurement){

  ## Rename for use in filter
  iq <- match_iq
  sn <- set_number
  sp <- split
  
  data <-
    sets_frame %>%
    filter(match_iq == iq
         , set_number == sn
         , split == sp)

  if(nrow(data) != 1)
    stop("something is wrong with your sets frame")

  full_set <- data$set[[1]]
  matched_set <- data$matched_set[[1]]
  pred <- data$pred[[1]]
  
  filter_vec <-
    pred(full_set$iq_native) | full_set$Dx == 0
    
  
  anat <- measures[[measurement]][,filter_vec]

  if(ncol(anat) != nrow(matched_set))
    stop("The filtration didn't work")

  list(data = matched_set
     , anat = anat
     , filter_vec = filter_vec)
}

fit_model <- function(model, data){
  weights <- data$data$weight
  anatLmer(model, data = data$data
         , anat = t(data$anat), weights = weights)
}

purge_environments <- function(mod){
  environment(attributes(mod)$mincLmerList[[1]]$formula) <- NULL
  environment(attr(attributes(mod)$mincLmerList[[1]]$fr, "formula")) <- NULL
  environment(attr(attributes(mod)$mincLmerList[[1]]$fr, "terms")) <- NULL
  
  mod
}

run_randomization <-
  function(i){
    gc()
    gc()

    mes <- randomization_experiments$measures[i]
    form <- randomization_experiments$model_string[[i]]
    set_n <- randomization_experiments$set_number[[i]]
    sp <- randomization_experiments$split[i]
    miq <- randomization_experiments$match_iq[i]
    
    data <- get_data(match_iq = miq, set_number = set_n
                   , split = sp, measurement = mes)

    shuf_ind <- randomization_experiments$shuffle[i]
    if(!is.na(shuf_ind)){
      subset_sexes <- new_sexes[complete_measures,]
      data$data$sex <-
        ifelse(subset_sexes[data$filter_vec,shuf_ind] == "M", 0, 1)

    } else {
      data$data$sex <- ifelse(data$data$sex == "M", 0, 1)
    }
    
    mod <- fit_model(as.formula(form), data)
    mod <- fit_model(as.formula(form), data)
    attr(mod, "anat") <- NULL
    mod <- purge_environments(mod)
    
    mod
  }
```
## Set up registry

Now to intialize the registry

```{r init_registry, cache = TRUE, dependson = c("setup_function", "generate_experiment_frame")}
sa_reg <-
    makeRegistry("spatial_analyses"
               , packages = c("autismSexDifferences"
                            , "RMINC"
                            , "purrr"
                            , "dplyr"))

sa_reg$cluster.functions <-
  makeClusterFunctionsTORQUE("torque.tmpl")

sa_reg$default.resources <- 
    list(nodes = 1
       , memory = "12G"
       , walltime = "08:00:00"
       , max.concurrent.jobs = 2000)

batchExport(reg = sa_reg
            , export = list(measures = measures
                          , randomization_experiments = randomization_experiments
                          , sets_frame = sets_frame
                          , fit_model = fit_model
                          , shuffles = shuffles
                          , get_data = get_data
                          , new_sexes = new_sexes
                          , purge_environments = purge_environments
                          , complete_measures = complete_measures
                            ))

sa_reg <- sa_reg
```

## Create Jobs

Add the jobs to the registry

```{r job_creation, cache = TRUE, dependson = "init_registry"}
job_ids <-
  batchMap(reg = sa_reg
         , run_randomization
         , seq_len(nrow(randomization_experiments)))

randomization_experiments$job_id <- job_ids$job.id

## job_ids[, chunk :=
##             chunk(seq_len(nrow(randomization_experiments))
##                 , chunk.size = 4)]

sa_reg <- sa_reg
```

## Test Job

Run a test job

```{r test_job, cache = TRUE, dependson = "job_creation"}
#invisible(testJob(reg = sa_reg, 20000)) 
```

## Run Jobs

Run the jobs and wait

```{r job_submission, cache = TRUE, dependson = "test_job"}
submitJobs(reg = sa_reg, job_ids)
waitForJobs(reg = sa_reg)
```

## Fix jobs that failed

```{r job_fixes, cache = TRUE, dependson = "job_submission"}
sa_reg <- loadRegistry("spatial_analyses", writeable = TRUE)

sa_reg$cluster.functions <-
  makeClusterFunctionsTORQUE("torque.tmpl")

sa_reg$default.resources <- 
    list(nodes = 1
       , memory = "12G"
       , walltime = "08:00:00"
       	 , max.concurrent.jobs = 2000)
	 
not_done <- findNotDone(reg = sa_reg)
submitJobs(reg = sa_reg, not_done)
waitForJobs(reg = sa_reg)
```

## Flag Finished

```{r finalize, cache = TRUE, dependson = "fixup"}
system("touch spatial_analyses_finished.txt")
```
